NMRlipids Databank makes data-driven analysis of biomembrane properties accessible for all

### 2023-03-09 main.tex
Update figures

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{Figures/overlay3.pdf}
    \caption{A) Schematic presentation of the overlay structure used in the NMRlipids databank. A more detailed structure of the databank layer is shown in Fig.~\ref{DatabankStructure} in the SI.
    %b) Distribution of the lengths of the trajectories, total number of trajectories and total length of the simulations in the NMRlipids databank.
    B) Distribution of lipids present in the trajectories in the NMRlipids databank. Lipids occuring in five or fewer simulations ('others') are listed on the right. 
    C) Distribution of force fields in the simulations in the NMRlipids databank. References for each force field are given in table~\ref{tab:ForceFields}.
    D) Currently available binary mixtures in the NMRlipids databank. 
    }
    \label{fig:overlay}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=88mm]{Figures/flowchart2.pdf}
    \caption{ A) Flowchart for performing an analysis of properties through all MD simulations in the NMRlipids databank using the API.
    B) Flowchart for accessing results calculated from the NMRlipids databank and stored to the application layer.
    C) Area per lipids of POPC and POPE lipid bilayers predicted by different force fields at 310\,K in simulations that are available in the NMRlipids databank. The points from the best performing simulations in the NMRlipids databank quality evaluation for each lipid (Figs.~\ref{fig:quality} and~\ref{fig:POPC_POPE_dataSI}) are surrounded by black circles. 
    }
    \label{fig:POPCPOPEapls}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=\linewidth]{Figures/quality3.pdf}
    \caption{ A) Best simulations ranked based on overall order parameter quality.
    B) Best simulations ranked based on the overall order parameter quality of POPE lipid. 
    C)--E) Evaluation against experimental (NMR order parameters and X-ray scattering ) data exemplified for a simulation with the best overall order parameter quality (C), the best quality for POPE lipid (D), and the headgroup quality for POPE (E).
    F) Scatter plots and Pearson correlation coefficients, $r$, for the membrane area per lipid, thickness, first minimum of X-ray scattering form factor and average order parameter of the {\textit sn}-1 acyl chain extracted from the NMRlipids databank. All correlation coefficients have p-value below 0.001 as indicated by $^{***}$. For more correlations see Fig.~\ref{fig:QualityCorrelationsSI}.
    }
    \label{fig:quality}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{Figures/overlay3.pdf}
    \caption{A) Schematic presentation of the overlay structure used in the NMRlipids databank. A more detailed structure of the databank layer is shown in Fig.~\ref{DatabankStructure} in the SI.
    %b) Distribution of the lengths of the trajectories, total number of trajectories and total length of the simulations in the NMRlipids databank.
    B) Distribution of lipids present in the trajectories in the NMRlipids databank. Lipids occuring in five or fewer simulations ('others') are listed on the right. 
    C) Distribution of force fields in the simulations in the NMRlipids databank. References for each force field are given in table~\ref{tab:ForceFields}.
    D) Currently available binary mixtures in the NMRlipids databank. 
    }
    \label{fig:overlay}
\end{figure}

@@

%\begin{figure}[t]
%    \centering
%    \includegraphics[width=88mm]{Figures/flowchart2.pdf}
%    \caption{ A) Flowchart for performing an analysis of properties through all MD simulations in the NMRlipids databank using the API.
%    B) Flowchart for accessing results calculated from the NMRlipids databank and stored to the application layer.
%    C) Area per lipids of POPC and POPE lipid bilayers predicted by different force fields at 310\,K in simulations that are available in the NMRlipids databank. The points from the best performing simulations in the NMRlipids databank quality evaluation for each lipid (Figs.~\ref{fig:quality} and~\ref{fig:POPC_POPE_dataSI}) are surrounded by black circles. 
%    }
%    \label{fig:POPCPOPEapls}
%\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=\linewidth]{Figures/quality5.pdf}
    \caption{ A) Best simulations ranked based on overall order parameter quality.
    B) Best simulations ranked based on the overall order parameter quality of POPE lipid. 
    C)--E) Evaluation against experimental (NMR order parameters and X-ray scattering ) data exemplified for a simulation with the best overall order parameter quality (C), the best quality for POPE lipid (D), and the headgroup quality for POPE (E).
    F) Scatter plots and Pearson correlation coefficients, $r$, for the membrane area per lipid, thickness, first minimum of X-ray scattering form factor and average order parameter of the {\textit sn}-1 acyl chain extracted from the NMRlipids databank. All correlation coefficients have p-value below 0.001 as indicated by $^{***}$. For more correlations see Fig.~\ref{fig:QualityCorrelationsSI}.
    }
    \label{fig:quality}
\end{figure}
